% Abstract page
\begin{center}
    \vspace*{2cm}
    {\Large \textbf{ABSTRACT}}\\[1cm]
\end{center}

This project presents "Introspection: Empowering Mental Health Support with Agentic AI," a WeChat Mini Program designed to provide non-clinical emotional support through natural language interaction. The system leverages agentic AI technologies and large language models (LLMs) to serve adolescent users in managing and reflecting on their emotions. The project addresses the significant supply-demand gap in China's psychological service industry, where professional resources are concentrated in tier-one cities with prohibitively high costs.

The system features multiple specialized AI agents working in concert to provide comprehensive mental health support. Key technical innovations include an Agentic RAG Framework for context-aware responses, comprehensive mood analysis, intelligent event extraction functionality, as well as history report generation for dynamic user interaction and structured recording. The technical implementation utilizes Meta-Llama-3.1-8B-Instruct model for natural language processing, Flask backend for API services, and WeChat Mini Program for the frontend interface. 

The system demonstrates the potential of AI-powered solutions in providing accessible, personalized, and stigma-free emotional support. Preliminary evaluations indicate emotional support effectiveness and the potential of agentic AI technology to provide accessible, low-cost mental health support while maintaining user privacy and data security. This project contributes to both technological advancement in AI-assisted therapy and practical solutions for mental healthcare accessibility.

\newpage 