% References
\newpage
\begin{thebibliography}{99}

\bibitem{weizenbaum1966} Weizenbaum, J. (1966). ELIZA—a computer program for the study of natural language communication between man and machine. \textit{Communications of the ACM, 9}(1), 36-45.

\bibitem{fitzpatrick2017} Fitzpatrick, K. K., Darcy, A., \& Vierhile, M. (2017). Delivering cognitive behavior therapy to young adults with symptoms of depression and anxiety using a fully automated conversational agent (Woebot): a randomized controlled trial. \textit{JMIR mental health, 4}(2), e19.

\bibitem{inkster2018} Inkster, B., Sarda, S., \& Subramanian, V. (2018). An empathy-driven, conversational artificial intelligence agent (Wysa) for digital mental well-being: real-world data evaluation mixed-methods study. \textit{JMIR mHealth and uHealth, 6}(11), e12106.

% not used
% \bibitem{touvron2023} Touvron, H., Lavril, T., Izacard, G., Martinet, X., Lachaux, M. A., Lacroix, T., ... \& Lample, G. (2023). LLaMA: Open and efficient foundation language models. \textit{arXiv preprint arXiv:2302.13971}.

% not used
% \bibitem{brown2020} Brown, T., Mann, B., Ryder, N., Subbiah, M., Kaplan, J. D., Dhariwal, P., ... \& Amodei, D. (2020). Language models are few-shot learners. \textit{Advances in neural information processing systems, 33}, 1877-1901.

% not used
% \bibitem{beck1979} Beck, A. T. (1979). \textit{Cognitive therapy and the emotional disorders}. Penguin.

% not used
% \bibitem{who2021} World Health Organization. (2021). \textit{Mental health atlas 2020}. World Health Organization.

% not used
% \bibitem{nhc2021} National Health Commission of the People's Republic of China. (2021). \textit{China's mental health development report}. Beijing: People's Medical Publishing House.

% not used
% \bibitem{li2023} Li, H., Zhang, R., Lee, Y. C., Kraut, R. E., \& Mohr, D. C. (2023). Systematic review and meta-analysis of AI-based conversational agents for promoting mental health and well-being. NPJ digital medicine, 6(1), 236. https://doi.org/10.1038/s41746-023-00979-5

% not used
% \bibitem{chen2024} Guo, Z., Lai, A., Thygesen, J. H., Farrington, J., Keen, T., \& Li, K. (2024). Large Language Models for Mental Health Applications: Systematic Review. JMIR mental health, 11, e57400. https://doi.org/10.2196/57400

\bibitem{xu2023large} Xu, D., Chen, W., Peng, W., Zhang, C., Xu, T., Zhao, X., ... \& Chen, E. (2024). Large language models for generative information extraction: a survey. \textit{Frontiers of Computer Science, 18}(6), 1-28.

\bibitem{golden2024describing} 
Golden, A., \& Aboujaoude, E. (2024). Describing the framework for AI tool assessment in mental health and applying it to a generative AI obsessive-compulsive disorder platform: Tutorial. \textit{JMIR Formative Research, 8}(1), e62963. JMIR Publications Inc., Toronto, Canada.

\end{thebibliography} 